\textbf{ A Sphere Model for Atrial Fibrillation}

### 2017-02-21 Literature Review/MSCI POSTER draft.tex
postert

\documentclass[twocolumn, a1paper, 20pt]{article}
 %\usepackage[scale=0.78,size=a1]{beamerposter}
%\setlength{\paperheight}{33.1in}
%\setlength{\paperwidth}{23.4in}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{adjustbox}
%\usepackage[sc]{mathpazo}
\usepackage[margin=0.5in]{geometry}
%\usepackage{multicol}
\usepackage{mathtools}
\usepackage{abstract}
\usepackage[compact]{titlesec}
\DeclareMathOperator{\sech}{sech}
\newcommand{\matr}[1]{\mathbf{#1}}
%\usepackage{placeins}
%\usepackage{textcomp}
\graphicspath{ {H:/} }

@@

  \item \textit{Excited state}: the muscle cell is excited by its excited neighbours and the Voltage of the cell is at its peak. 
  \item \textit{Refractory state} :the muscle cell goes through a phase during which it can't be excited again/
\end{itemize}

Where the refractory period depends on the last time a cell was excited.\\

@@

\section{\textbf{Kim Christensen Model}}

@@

\section{\textbf{Implementing Restitution in Kim Christensen Model}}

\section{\textbf{Kim Christensen model on a Sphere}}

>>>>

\documentclass[twocolumn, a1paper, 12pt]{article}
 %\usepackage[scale=0.78,size=a1]{beamerposter}
%\setlength{\paperheight}{33.1in}
%\setlength{\paperwidth}{23.4in}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{adjustbox}
%\usepackage[sc]{mathpazo}
\usepackage[margin=0.5in]{geometry}
%\usepackage{multicol}
\usepackage{mathtools}
\usepackage{abstract}
\usepackage[compact]{titlesec}
\DeclareMathOperator{\sech}{sech}
\newcommand{\matr}[1]{\mathbf{#1}}
%\usepackage{placeins}
%\usepackage{textcomp}
\graphicspath{ {H:/} }

@@

  \item \textit{Excited state}: the muscle cell is excited by its excited neighbours and the Voltage of the cell is at its peak. 
  \item \textit{Refractory state} :the muscle cell goes through a phase during which it can't be excited again - this period is called \textit{refractory period)}.
\end{itemize}

Where the refractory period depends on the last time a cell was excited and is always fixed to a constant.\\

@@

\section{\textbf{Kim Christensen's Model}}

@@

\section{\textbf{Implementing Restitution }}

Even though in Prof.Christensen model, the refractory period of each muscle cell was always fixed, this is not what happens in a real heart.
In a real heart the refractory period depends on the heart beat rate and on the last time each cell it was excited. The relationship between refractory period and heart beat rate is called restitution.
\\
In the first part of our project, we implemented restitution in Kim Christensen model in order

\section{\textbf{Kim Christensen's model on a Sphere}}
